Scale Space Edge Detection

### 2018-03-10 paper.tex
Move epsilon definition to fix error

Next, we check if the lines defined by our two zero conditions intersect.
\begin{lstlisting}
        intersect = segment_intersect(Z1_zeros..., Z2_zeros..., epsilon)
        if isnull(intersect)
            continue
        end
\end{lstlisting}
To do this, we calculate the distance between the lines defined by each isosurface.
If the segments are parallel, the distance is not defined, so we skip the face.
Next, we check that the lines intersect.
\begin{lstlisting}
        const epsilon = 10 * eps()
        distance, midpoint = get(intersect)
        if distance > epsilon || !all(1 - epsilon .<= midpoint .<= 2 + epsilon)
            continue
        end

>>>>

Next, we check if the lines defined by our two zero conditions intersect.
\begin{lstlisting}
        const epsilon = 10 * eps()
        intersect = segment_intersect(Z1_zeros..., Z2_zeros..., epsilon)
        if isnull(intersect)
            continue
        end
\end{lstlisting}
To do this, we calculate the distance between the lines defined by each isosurface.
If the segments are parallel, the distance is not defined, so we skip the face.
Next, we check that the lines intersect.
\begin{lstlisting}
        distance, midpoint = get(intersect)
        if distance > epsilon || !all(1 - epsilon .<= midpoint .<= 2 + epsilon)
            continue
        end
